---
title: "Regional temperature index for EBS salmon"
author: K. K. Holsman & E. Yasumiishi
output:
  pdf_document:
    fig_caption: yes
    fig_height: 4
    fig_width: 5
    highlight: tango
    keep_tex: yes
    latex_engine: xelatex
    toc: TRUE
  word_document:
    fig_caption: yes
    fig_width: 4
    keep_md: yes
  header-includes:
  - \usepackage{inputenc}
  - \usepackage{unicode-math}
  - \pagenumbering{gobble}
  html_document:
    df_print: kable
    fig_caption: yes
    theme: flatly
    toc: true
    toc_float: true
---

```{r startup, eval=TRUE, echo=FALSE, results='hide',message=FALSE}
 
 #source("R/make.R")       # loads packages, data, setup, etc.
 knitr::opts_chunk$set(echo = T, fig.align="center")
 thisYr <- format(Sys.time(), "%Y")
 today  <- format(Sys.time(), "%b %d, %Y")
 
     # --------------------------------------
    # SETUP WORKSPACE

    tmstp  <- format(Sys.time(), "%Y_%m_%d")
    main   <- getwd()  #"~/GitHub_new/ACLIM2"
    
    setwd("../")
    # loads packages, data, setup, etc.
    suppressWarnings(source("R/make.R"))
    setwd(main)
    
    # --------------------------------------
    
 
```

Last updated:  `r today`


# Overview

The code below steps through generating temperature indices from the Bering10K ROMSNPZ model hindcast and projections under NOAA's [**ACLIM project**](https://www.fisheries.noaa.gov/alaska/ecosystems/alaska-climate-integrated-modeling-project) for the Bering Sea. For more information see the ![The ACLIM Repository [**github.com/kholsman/ACLIM2**](https://github.com/kholsman/ACLIM2 "ACLIM2 Repo") which contains R code and Rdata files for working with data generated from the [**downscaled ROMSNPZ modeling**](https://beringnpz.github.io/roms-bering-sea) of the ROMSNPZ Bering Sea Ocean Modeling team; Drs. Hermann, Cheng, Kearney, Pilcher,Ortiz, and Aydin. *See [Hollowed et al. 2020](https://www.frontiersin.org/articles/10.3389/fmars.2019.00775/full) for more information about the ACLIM project.*

The goal of this vignette is to outline the steps taken to develop the temperature indices used as covariates in EBS salmon population dynamics models. 

# Creating covariates (annual indices; bias corrected & z-scored)

## 1) Create hindcast and historical indices

```{r annual_aclim_indices, eval=F, include=T,echo=T}
    
    # Create annual indices 
    # the code below creates annual indices and 
    # bias corrects them to a reference period or historical runs

    tmstamp1  <- format(Sys.time(), "%Y%m%d")
    tmstamp1  <- "20211104"
    update_hind  <- TRUE   # set to true to update hind and hindS; needed annually
    update_proj  <- TRUE   # set to true to update proj and projS; not needed
    update_hist  <- TRUE   # set to true to update proj and projS; not needed
    # identify the year to z-score scale / delta
    deltayrs     <- 1970:2000

    cat("making annual indices, please wait....\n")
     # now create annual indices from the regional polygon weekly values:
     # this step is slow.....about 4 mins per simulation
    
    # remove these variables:
    vl <- srvy_vars[!srvy_vars%in%c("station_id","latitude","longitude","stratum","doy",
                                      "Iron_bottom5m","Iron_integrated","Iron_surface5m",
                                      "prod_Eup_integrated","prod_NCa_integrated")]
    
      # Identify which variables would be normally distributed
     normvl <- c("shflux","ssflux","temp_bottom5m",
      "temp_integrated","temp_surface5m",
      "uEast_bottom5m","uEast_surface5m",
      "vNorth_bottom5m","vNorth_surface5m")
    
    normlist <- data.frame(var = vl, lognorm = TRUE)
    normlist$lognorm[normlist$var%in%normvl] <- FALSE

    if(update_hind){
       source("R/sub_scripts/make_hind.R")
    }else{
      load(file.path(main,"Data/out",paste0("hind_",tmstamp1,".Rdata")))
      head(hind)
    }
    
    if(update_hist){
       source("R/sub_scripts/make_hist.R")
    }else{
     load(file.path(main,"Data/out",paste0("hist_CMIP6_raw_",tmstamp1,".Rdata")))
      hist_raw <- hist2; rm(hist2)
      load(file.path(main,"Data/out",paste0("hist_CMIP6_BiasCorr_",tmstamp1,".Rdata")))
      hist <- hist2; rm(hist2); head(hist)
    }
```


## 2) Create proj indices


```{r annual_aclim_indices_proj, eval=F, include=T,echo=T}
    
   if(update_proj){
     source("R/sub_scripts/make_proj.R")
   }else{
     load(file.path(main,"Data/out",paste0("proj_CMIP6_BiasCorr_",tmstamp1,".Rdata")))
     projCMIP6 <- proj; rm(proj)
     load(file.path(main,"Data/out",paste0("proj_CMIP6_raw_",tmstamp1,".Rdata")))
     proj_raw<-proj; rm(proj)
     load(file.path(main,"Data/out",paste0("proj_CMIP5n6_BiasCorr_",tmstamp1,".Rdata")))
     head(proj)
   }
  
    # now add gcm and ssp:
   proj      <- add_gcmssp(proj)
   proj_raw  <- add_gcmssp(proj_raw)
   projCMIP6 <- add_gcmssp(projCMIP6)
   
   
   hind$cmip     <- "hindcast"
   hind$scenario <- "hindcast"
   hind$gcm      <- "CORECFS"
   hind$ssp      <- "hindcast"
  
   
```

## 3) Z-score & bias correc the data

```{r annual_aclim_indices_zscore, eval=F, include=T,echo=T}
   
   # Zscore-scale  the data
   # -------------------------------------
      hindS <- ScaleIT(proj_dat = hind,
                     ref_dat  = hind,
                     ref_yrs  = deltayrs)
    
      tmpfl <- file.path("Data/out/",paste0("hind_delta_",tmstamp1,".Rdata"))
      if(file.exists(tmpfl)) file.remove(tmpfl)    
      save(hindS, file=tmpfl)
      rm(tmpfl)
    
      projS <- ScaleIT(proj_dat = proj,
                     ref_dat  = hind,
                     ref_yrs  = deltayrs)
     
      tmpfl <- file.path("Data/out/",paste0("proj_CMIP6_BiasCorr_delta_",tmstamp1,".Rdata"))
      if(file.exists(tmpfl)) file.remove(tmpfl)    
      save(projS, file=tmpfl)
      rm(tmpfl)
    
     
    # now add gcm and ssp:
    # -------------------------------------
    simset <- data.frame(sim=unique(proj$sim),stringsAsFactors =  FALSE)
    ttp   <- strsplit(
      sapply(strsplit(simset$sim,split=
                      "_B10K-K20P19_"),"[[",2),"_")
    simset$cmip <- sapply(ttp,"[[",1)
    simset$gcm  <- sapply(ttp,"[[",2)
    simset$ssp  <- sapply(ttp,"[[",3)
    
    CMIP6set    <- simset$sim[simset$cmip =="CMIP6"]
    
    
     # Now make files for .dat input:
    # -----------------------------
    shortvars <- c("Cop_integrated","PhL_integrated",
    "EupS_integrated","largeZoop_integrated","NCaS_integrated",
    "salt_surface5m","temp_bottom5m","temp_surface5m")

    longvars <- c("Ben","Cop_integrated","DetBen","EupO_integrated", 
    "EupS_integrated", "hice","Jel_integrated","largeZoop_integrated",
    "MZL_integrated","NCaO_integrated"  ,"NCaS_integrated"  , "PhL_integrated",
    "PhS_integrated"    ,"salt_surface5m","shflux","ssflux","temp_bottom5m",
    "temp_integrated","temp_surface5m" ,"uEast_bottom5m","uEast_surface5m",
    "vNorth_bottom5m","vNorth_surface5m")
    
    short_vars <- makeROMSNPZdat(outfldr = "Data/out",
                   hind_fl    = projS,
                   proj_fl    = hindS,
                   hind_sheetnames = c("K20_CORECFS"), 
                   hinddat    = "hind",
                   projdat    = "proj",
                   hind_years = 1979:thisYr,
                   proj_years = (thisYr+1):2099,
                   varsIN     = shortvars,
                   nsppIN     = 3,
                   write2dat  = T,
                   seasonsIN  = c("Winter","Spring","srvy_rep","Fall"),
                   datfile    = paste("_romspz",thisYr,"_short.dat"))
    
    # now make some plots:
    # ----------------------
    
    if(update.figs)
      #source(file.path(main,"R/sub_scripts/make_annual_plots.R"))
    
    if(update.figs)
      source(file.path(main,"R/sub_scripts/make_summary_plots.R"))
    
    # plot Fall values:
    # -----------------------------
  
   
    pfall_BT_fut
     if(update.figs){
        sclr <- 1.2
        jpeg(file=file.path(main,"Figs/Fall_temperature_fut.jpg"),
             width=7*sclr,height=5*sclr, res=150, units="in")
        print(pfall_BT_fut)
        dev.off()
     }
    
    psrvy_BT_fut
     if(update.figs){
        sclr <- 1.2
        jpeg(file=file.path(main,"Figs/Srvy_temperature_fut.jpg"),
             width=7*sclr,height=5*sclr, res=150, units="in")
        print(psrvy_BT_fut)
        dev.off()
     }
    
    pfall_BT_fut_raw
     if(update.figs){
        sclr <- 1.2
        jpeg(file=file.path(main,"Figs/Fall_temperature_raw_fut.jpg"),
             width=7*sclr,height=5*sclr, res=150, units="in")
        print(pfall_BT_fut_raw)
        dev.off()
     }

   pfall_BT_fut_scaled
   if(update.figs){
      sclr <- 1.2
      jpeg(file=file.path(main,"Figs/Fall_temperature_scaled_fut.jpg"),
           width=7*sclr,height=5*sclr, res=150, units="in")
      print(pfall_BT_fut_scaled)
      dev.off()
   }
  
   z6_fut2 <- plotROMZ(
                      hindIN = hind%>%filter(season=="Fall",
                          var%in%c("EupS_surface5m"),
                          year<=thisYr),
                      futIN  = proj%>%filter(season=="Fall",
                         var%in%c("EupS_surface5m"),
                         sim%in%CMIP6set,
                         year>=thisYr),
                      plotval  = "value",
                      refYrsIN = deltayrs,
                      scalesIN ="free",
                      simsetIN = simset%>%filter(sim%in%CMIP6set),
                      titleIN  = "Surface EuphS (srvy_rep) ")
    z6_fut2
Euhp_Fall_fut
     if(update.figs){
        sclr <- 1.2
        jpeg(file=file.path(main,"Figs/Fall_EuphSIntg_fut.jpg"),
             width=7*sclr,height=4*sclr, res=150, units="in")
        print(Euhp_Fall_fut)
        dev.off()
     }
    Euhp_Fall_fut_raw
    
     if(update.figs){
        sclr <- 1.2
        jpeg(file=file.path(main,"Figs/Fall_EuphSIntg_fut_raw.jpg"),
             width=7*sclr,height=4*sclr, res=150, units="in")
        print(Euhp_Fall_fut_raw)
        dev.off()
     }
  # 

```


# Recentering and bias correcting covariates

# Plotting covariate results


